Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2024-01-22 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c } 
            \input{output/chandra-obs-table.tex}
        \end{tabular}
        \label{tab:chandra_obs}
        \script{chandra-obs-table.py}
        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}}
    \end{table}

>>>>

    \begin{table}
    \centering
        \begin{tabular}{ c|c|c|c|c } 
            \input{output/chandra-obs-table.tex}
        \end{tabular}
        \label{tab:chandra_obs}
        \script{chandra-obs-table.py}
        \caption{Observation list and details from the Chandra example analysis in Section~\ref{sec:chandra-example}. The relative exposure columns list the exposure for each observation expressed as the ratio with the exposure of the reference observation with obs ID 8365. The }
    \end{table}
